Accurate plant pathogen effector protein classification _ab initio_ with **deepredeff**, an ensemble of convolutional neural networks.

### 2020-06-08 main.Rmd
Fixed #7 and #8

---
title: "Accurate plant pathogen effector protein classification _ab initio_ with **deepredeff**, an ensemble of convolutional neural networks."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm_latex.tex
    toc: no
fontsize: 12pt
fontfamily: sans
papersize: a4paper
author:
  - name: Ruth Kristianingsih, Dan MacLean
  - affiliation: The Sainsbury Laboratory, University of East Anglia, Norwich Research Park, Norwich, UK, NR4 7JJ, dan.maclean@tsl.ac.uk
abstract: "TBD."
geometry: margin=1in
biblio-style: apsr
bibliography: ["r-references.bib", "r-packages.bib"]
graphics: yes
header-includes:
  - \usepackage{amsmath}
  - \usepackage{siunitx}
---

@@

# Build R pacakges Bib build
r_refs(file = "r-packages.bib")

@@

heatmap_linebar_oomycete <- oomycete_heatmap %>%
  dplyr::mutate(index = V1 + 1) %>%
  dplyr::filter(index <= 750) %>%
  dplyr::select(index, heatmap_oomycete_smooth) %>%
  ggplot(aes(x = index, y = heatmap_oomycete_smooth)) +
  geom_line() +
  geom_vline(xintercept = 15, linetype = 'dashed', color = "blue") +
  geom_vline(xintercept = 40, linetype = 'dashed', color = "blue") +
  geom_vline(xintercept = 45, linetype = 'dashed', color = "red") +
  geom_vline(xintercept = 70, linetype = 'dashed', color = "red") +
  scale_x_continuous(breaks = seq(0, 750, 150)) +
  labs(x = 'Position', y = "Value") +
  ggplot2::labs(tag = "B")

heatmap_linebar_fungi <- fungi_heatmap %>%
  dplyr::mutate(index = V1 + 1) %>%
  dplyr::filter(index <= 750) %>%
  dplyr::select(index, heatmap_fungi_smooth) %>%
  ggplot(aes(x = index, y = heatmap_fungi_smooth)) +
  geom_line() +
  geom_vline(xintercept = 35, linetype = 'dashed', color = "blue") +
  geom_vline(xintercept = 80, linetype = 'dashed', color = "blue") +
  scale_x_continuous(breaks = seq(0, 750, 150)) +
  labs(x = 'Position', y = "Value") +
  ggplot2::labs(tag = "C")

>>>>

---
title: "Accurate plant pathogen effector protein classification _ab initio_ with **deepredeff**, an ensemble of convolutional neural networks."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm_latex.tex
    toc: no
fontsize: 12pt
fontfamily: sans
papersize: a4paper
author:
  - name: Ruth Kristianingsih, Dan MacLean
  - affiliation: The Sainsbury Laboratory, University of East Anglia, Norwich Research Park, Norwich, UK, NR4 7JJ, dan.maclean@tsl.ac.uk
abstract: "TBD."
geometry: margin=1in
biblio-style: apsr
bibliography: ["r-references.bib"]
graphics: yes
header-includes:
  - \usepackage{amsmath}
  - \usepackage{siunitx}
---

@@

# Build R pacakges Bib build
papaja::r_refs(file = "r-references.bib")

@@

heatmap_linebar_oomycete <- oomycete_heatmap %>%
  dplyr::mutate(index = V1 + 1) %>%
  dplyr::filter(index <= 750) %>%
  dplyr::select(index, heatmap_oomycete_smooth) %>%
  ggplot(aes(x = index, y = heatmap_oomycete_smooth)) +
  geom_line() +
  geom_vline(xintercept = 15, linetype = 'dashed', color = "blue") +
  geom_vline(xintercept = 40, linetype = 'dashed', color = "blue") +
  geom_vline(xintercept = 45, linetype = 'dashed', color = "red") +
  geom_vline(xintercept = 70, linetype = 'dashed', color = "red") +
  scale_x_continuous(breaks = seq(0, 750, 150)) +
  labs(x = 'Position', y = "Value") +
  ggplot2::labs(tag = "C")

heatmap_linebar_fungi <- fungi_heatmap %>%
  dplyr::mutate(index = V1 + 1) %>%
  dplyr::filter(index <= 750) %>%
  dplyr::select(index, heatmap_fungi_smooth) %>%
  ggplot(aes(x = index, y = heatmap_fungi_smooth)) +
  geom_line() +
  geom_vline(xintercept = 35, linetype = 'dashed', color = "blue") +
  geom_vline(xintercept = 80, linetype = 'dashed', color = "blue") +
  scale_x_continuous(breaks = seq(0, 750, 150)) +
  labs(x = 'Position', y = "Value") +
  ggplot2::labs(tag = "B")
